\documentclass{article}
%easy margins
\usepackage[top=.2in, bottom=.4in, left=.8in, right=.8in]{geometry}
%http links in text
\usepackage{hyperref}
%pictures
\usepackage{graphicx}
%quotes
\usepackage{csquotes}
%landscape single pages
\usepackage{lscape}
%inline enumeration
\usepackage[inline]{enumitem}
\usepackage{setspace}
%****************************************************************
% changing font family
\renewcommand{\familydefault}{\sfdefault} %change font

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Adding title and authors
%\title{Cell classification by applying graphlets on HiC data}
%\author{Behnam Rasoolian  \and Liangliang Xu \and Zheng Zhang}
%\date{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chaning font to a local font
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%page title
%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%micromanage font size, the first argument is
%%size of the font, the second line distance
\fontsize{11pt}{26pt}\selectfont

%No page numbers.
\pagenumbering{gobble}
%no indentaion for new paragraphs.
\setlength{\parindent}{0pt}
Good Afternoon Dr. ....,

I am a masters student at Auburn University. I am supervised by Dr. 
Bhattacharya. I am conducting research on HiC datasets. Specifically, 
I am looking at local differences between normal and leukemic cells.
In my research I am using your datasets from the link below:

\url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_ genome_data/}

I am emailing you since I have a question that I haven't been 
able to resolve. I have been trying different normalization methods on HiC
contact matrices that I have extracted from datasets in link  above
; however, I haven't be able to reproduces contact files that
are here: 

\url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/unzipped/Input/HiC/}

I have tried sequential component normalization (SCN)
and pearson correlation but the results are not as smooth
and clean as the ones in the link above. For the sake of reproductibility,
could you let me know how such normalizations were made on the original
HiC contact maps? I would greatly appreciate your response since it will
be a great help in my research.

{\small
\setstretch{0.5}
Regards,\\
Behnam Rasoolian\\
M.Sc. student in Computer science and Software Engineering\\
Auburn University\\
}

\texttt{test.py} \\
I have been playing with HiC data some more. I have tried setting the 
values on and around the main diagonal to 0 and calculate pearson 
correlation matrix. The results where somehow smooth but not quitely.
The constact map corresponding to contact\_All dataset set shows
a smoothness close to what I am seeking.
I have also tried to perform linear transformation on one HiC data 
to 
\end{document}
